Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/paper.Rmd
rephrase spatial blocking intro

The "Spatial blocking" from package \pkg{blockCV} comes with various options to customize the zone creation.
Besides the choice of relying on an initial random  (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`) for the final partition aggregation, support for SDM specific background data is built-in.
Supplying a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) will create a quadratic block pattern across the study area.
Ultimately, users can also supply a user-defined polygon which defines the zones.

After the initial block creation, multiple "blocks" are combined to form a partition, honoring the number of folds requested by the user.
For example, in a five-fold scenario with a grid of four columns and five rows, the method would combine one fifth of all blocks (= four blocks) into a single partition.

>>>>

The "Spatial blocking" from package \pkg{blockCV} comes with various blocking options such as random (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`).
However, instead of using these options, the user might also supply a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) which will create a quadratic block pattern across the study area.
<!--JM: to stay consistent please add the argument which lets the user indicate a user-defined polygon-->
This kind of blocking might be of special interest for SDM studies as well as the possibility to supply a user-defined polygon with predefined blocking zones.

After the initial block creation, multiple "blocks" are combined to form a partition in correspondence with the number of folds requested by the user.
For example, in a five-fold scenario with a grid of four columns and five rows, the method would combine one fifth of all blocks (= four blocks) into a single partition.
